\chapter*{General Introduction}
\addcontentsline{toc}{chapter}{General Introduction}

\section*{Context and Application Domain}
This project was carried out at \textbf{Canny Vision}, a startup that specializes in computer vision solutions. The company provides a wide range of AI services, including shoplifting detection, tracking traffic violations, and performing data analysis on retail customers—such as calculating the average time spent in specific aisles based on people entering and exiting the shop.

\section*{Problem Statement and Motivation}
For a company of this size and technical nature, it is mandatory to use a system that tracks progress, tickets, and business objectives. While there are many popular market solutions like Jira and ClickUp that offer great UI/UX design and numerous features, Canny Vision cannot tolerate storing its data on external servers. This represents a significant security issue and creates a risky reliance on third-party companies, which is unacceptable for a firm handling sensitive surveillance data.

\section*{Project Objectives and Expected Deliverables}
Because of these security concerns, I was assigned the responsibility of developing a custom \textbf{Ticket Management System (TMS)} tailored specifically to the company's needs. The primary objective was to deliver a secure platform built with a \textbf{Zero Trust architecture}, ensuring that all necessary security measures are handled internally to maintain absolute control over the data.

\section*{Summary of Work Completed}
During this internship, I developed the full system using a stack consisting of \textbf{Jakarta EE}, \textbf{WildFly} and \textbf{Vanilla JS}. The work involved designing the core architecture, implementing custom security interceptors for fine-grained access control, and building a responsive interface that meets the operational needs of the Canny Vision team. The application is also delivered as a \textbf{Progressive Web App}, meaning team members can consult their tickets and epics offline and receive push notifications when a ticket is assigned to them.

\section*{Chapter-by-Chapter Roadmap}
This report is organized into four main chapters as follows:
\begin{itemize}
    \item \textbf{Chapter 1: State of the Art} provides a review of existing solutions and the technical context of the project.
    \item \textbf{Chapter 2: Architecture and Conception} details the design phase and the proposed technical solution.
    \item \textbf{Chapter 3: Environment and Realisation} describes the tools used and the actual implementation phase of the system.
    \item \textbf{Chapter 4: Analysis, Tests, and Performance Evaluation} presents the testing results and an evaluation of the system's efficiency.
\end{itemize}

Finally, the report ends with a \textbf{Conclusion} summarizing the results of the internship and potential future improvements.