\chapter*{Foreword}
\addcontentsline{toc}{chapter}{Foreword}

This report presents the work carried out during my final year internship at \textbf{Canny Vision}, a company specialising in computer vision solutions. The internship ran from \textbf{16 February 2026 to 12 June 2026}, under the supervision of \textbf{Mr Mohamed-Bêcha Kaaniche} as external supervisor and \textbf{Mr Mourad Menif} as academic supervisor. The main focus of the project was to design and develop a Ticket Management System (TMS) tailored to the specific operational and security needs of Canny Vision's teams.

\bigskip

It is with sincere appreciation that I dedicate these lines to everyone who contributed, directly or indirectly, to the completion of this work.

I would like to express my gratitude to Mr~Kaaniche for his guidance, availability, and constructive feedback throughout the project. His support at every stage of development was genuinely valuable.

I would also like to thank Mr~Menif for his advice and academic perspective, which helped me maintain a clear view of the broader context of the work.

My thanks go to \textbf{SUP'COM} for the academic foundation it provided and for the opportunity to apply engineering principles in a real professional environment.

Finally, I extend my appreciation to the jury members who will take the time to read and evaluate this report.

\bigskip\bigskip

\noindent\textbf{Responsible AI Use Declaration.}
Generative AI tools (Claude) were used during the preparation of this report for language improvement, LaTeX formatting, and structuring certain sections. All technical content, design decisions, implementation work, and analysis are entirely my own. The report faithfully reflects my understanding and the work I carried out during the internship.
